Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-26 exec-model.tex
New figure
exec model
better latency figure

\begin{figure}[t!]
\centering
\includegraphics[width=.7\textwidth]{figs/dataflow}
\vspace{-3mm}
\caption{A simple dataflow graph comprising stateful operators (sources, sinks and operators), and intermediate streams (transient and materialized).}
\label{fig:dataflow}
\end{figure}

@@

\para{Balancing Latency and Throughput.} Flink’s data exchange mechanisms are implemented around the exchange of buffers. When a data record is ready on the producer side, it is serialized and stored into one or more buffers that can be forwarded to consumers. A buffer in Flink is sent to a consumer either i) as soon as it is full, or ii) when a timeout condition is reached. This enables Flink to achieve, high throughput by setting the size of buffers to a high value, e.g., a few kilobytes, as well as low latency by setting the buffer timeout to a low value e.g., a few milliseconds.

>>>>

\begin{figure}[t!]
\begin{minipage}{1.1\linewidth}
      \centering
       \hspace{-0.1\linewidth}
      \begin{minipage}{0.55\linewidth}
        \begin{figure}[H]
        \centering
        \includegraphics[width=.999\textwidth]{figs/dataflow}
        \vspace{-3mm}
        \caption{A simple dataflow graph.}
        \label{fig:dataflow}
        \end{figure}
      \end{minipage}
      \hspace{0.03\linewidth}
      % \vspace{-3mm}
      \begin{minipage}{0.32\linewidth}
          \begin{figure}[H]
				\includegraphics[width=.99\textwidth]{figs/latency-throughput.pdf}
				\vspace{-1mm}
    			\caption{The effect of buffer-timeout in latency and throughput.}
    			\label{fig:latency-throughput}
          \end{figure}
      \end{minipage}
  \end{minipage}
\end{figure}

@@

\para{Balancing Latency and Throughput.} Flink’s data exchange mechanisms are implemented around the exchange of buffers. When a data record is ready on the producer side, it is serialized and stored into one or more buffers that can be forwarded to consumers. A buffer in Flink is sent to a consumer either i) as soon as it is full, or ii) when a timeout condition is reached. This enables Flink to achieve, high throughput by setting the size of buffers to a high value, e.g., a few kilobytes, as well as low latency by setting the buffer timeout to a low value e.g., a few milliseconds. \autoref{fig:latency-throughput} shows the effect of buffer-timeouts to the throughput and latency of delivering records in a simple streaming grep job on 30 machines (120 cores). Flink can achieve an observable 99-th percentile latency of 20 milliseconds. The corresponding throughput is 24,500 events per second per core. As we increase the buffer timeout, we see an increase in latency with an increase in throughput, until full throughput is reached (where buffers fill up faster than the timeout expiration). At a buffer timeout of 50 milliseconds, the system reaches full throughput of 750,000 events per second per core with a 99-th percentile latency of 50 milliseconds.
